Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-24 paper/datasheet_project_gutenberg.qmd
final paper and datasheet updates

	- Yes, the relationships between individual instances are made explicit through their eponymously titled labels and the book IDs as provided from Project Gutenberg, which helps amalgamate data by each individual SOC text. 

>>>>

	- Yes, the relationships between individual instances are made explicit through their eponymously titled labels and the book IDs as provided from Project Gutenberg, which helps clarify which data belongs to which individual SOC text. 

### 2024-04-24 paper/paper.qmd
final paper and datasheet updates

Next, custom datasets containing each author's raw texts were created. This involved using the identification number of the desired literary work and the `gutenberg_download` function to retrieve the HTML texts. Subsequently, the data was saved into individual Parquet datasets, as demonstrated in @tbl-joyce.

@@

Next, in @tbl-joyce-token, to measure the word count of each literary text, we first tokenized or separated each text into individual chunks of words using `unnest_tokens()` [@rTidytext].In addition, to account for stop words like, a, of, and, etc., the dataset `stop_words`and the function `anti_join` from @rTidytext were used to exclude all stop words from the self-generated datasets of SOC texts, ensuring data validity and meaningful analysis.

>>>>

Next, custom datasets containing each author's raw texts were created. This involved using the identification number of the nine desired literary works and the `gutenberg_download` function to retrieve the HTML texts. Subsequently, the data was saved into individual Parquet datasets, as demonstrated in @tbl-joyce.

@@

Next, in @tbl-joyce-token, to measure the word count of each literary text, we first tokenized or separated each text into individual chunks of words using `unnest_tokens()` [@rTidytext]. In addition, to account for stop words like, a, of, and, etc., the dataset `stop_words`and the function `anti_join` from @rTidytext were used to exclude all stop words from the self-generated datasets of SOC texts, ensuring data validity and meaningful analysis.
